Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-15 Ben_Manuscripts/structure_paper/Draft.tex
Edits

  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
  In 2016, Feng et al. showed that one could obtain the same result using a second
  technique termed soft confinement\cite{feng_thin_2016}. Current experimental 
  efforts are focused on extending the method to the H\textsubscript{II} phase 
  and characterizing the performance of these newly aligned systems.

@@

  In this paper, we develop a molecular model of the Col\textsubscript{h} assembly 
  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which will allow us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. We will use this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
	relative intensity.  Accordingly, we name these reflection R-spots. The
	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
	respective quadrants. In many liquid crystal systems one can explain the spots
	as the product of alkane chains tilted with respect to the membrane
	plane\cite{govind_simple_2001}.

@@

    %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
    % in many liquid crystal systems?
    %BJC5: changed to 'many liquid crystalline systems'
 	We are careful to avoid the term 'layers' since many liquid crystalline systems
 	have long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
    %MRS7: look carefully at tenses.  Don't describe the research in future tense. 
    % if it's describing your presentation of the research in the paper , use present tense. 
    % If it's describing something you did, use past tense. I changed some of them, but not all.
 	%We will use 
    In this study, we use our atomistic molecular model to study how the system's structure is 
    affected by the density of monomers surrounding each pore's hydrophilic core.

@@

@@

	The limited picture that experiment provides tells us that there are hexagonally packed, 
	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
	regions as tube-like pathways with well-defined boundaries. We explored the composition
	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
	sensitivity to initial configuration.

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water may be leached into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
	to see if there is any meaningful structural difference between a "dry" and "wet" system.

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended
  periodically. Each pore is made of columns of stacked monomers with periodic
  continuity along the pore axis, avoiding any edge effects and creating an
  infinite length pore ideal for studying transport. We prefer a small number of stacked
  monomers in order to reduce computational cost and to allow us to look at
  longer timescales. Ultimately, we chose to build a system with 20 monomers
  per column in order to obtain sufficient resolution when simulating
  X-ray diffraction patterns (see further discussion in section S\ref{S-section:monomers_per_column}).
  %MRS7: refer to supporting information (if it's there) for more discussion on stability as a function of height?
  %BJC6: gave it a shot in supplemental

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. The initial distance between pores, within a wide range, also has 
  little effect on the the equilibrated structure. However, one should not start them
  too close or there will be high energy repulsions during early equilibration. We 
  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
  Supporting information, section S\ref{S-section:initial_config_dependence}. The 
  distance between vertically stacked monomers, the position of monomers with respect 
  to vertically adjacent monomers, and the number of columns per pore do influence the 
  equilibrated structure and require further justification for their choices. We rely on 
  experimental data to inform them.

  We chose the vertical spacing between monomers for the initial configuration based
  on R-$\pi$ and then allowed the system to readjust during equilibration. Each monomer was
  rotated so the plane of its aromatic head group would be coplanar with the xy plane. We
  explored three different initial monomer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial spacing of 5
  \AA. We briefly explored a third system with an initial spacing of 10
  \AA. However this spacing yields non-physical behavior which is detailed in the 
  Supporting Information, section S\ref{S-section:initial_dbwl}.

@@

  \subsection{Equilibration}
  %MRS7: could put this mostly in supporting. 
  %BJC6: cut in half
  We developed equilibration schemes for creating dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. For wet systems, the desired concentration of water was added to 
  the initial configuration and we carried out equilibration in the same way
  as the dry systems. First, we fixed monomer head groups in place using position
  restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We gradually
  released the position restraints by decreasing the force constants over a series
  of simulations. We allowed the resulting unrestrained structure to equilibrate for
  5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
  followed by NPT equilibration simulations run for at least 400 ns using the 
  Parrinello-Rahman barostat. More precise details are available in 
  section S~\ref{S-section:equilibration}.

@@

  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
  average distance between stacked monomers, and an amplitude that decays exponentially
  (See Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
  to a decaying exponential function of the form:
  \begin{equation}
  	Ae^{-z/L}
  	\label{eqn:decaying_exponential}
  \end{equation}
  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
  and L is the fit correlation length. We calculated the error in the estimated value
  of L as the square root of the diagonal entry of the covariance matrix of 
  optimized fit parameters.

@@

  We explored the pores' compositions by measuring the average number densities
  of various monomer components as a function of distance from the pore centers.
  We looked at the average number density of sodium ions, aromatic rings and 
  carbon atoms making up the monomer tails. We binned the radial distance of all
  atoms in each group from the pore centers, then normalized by the area of the
  annulus defined by the bin edges and the z box vector (See Figure~S\ref{S-fig:rdf_diagram}).

@@

  We normalized all diffraction patterns relative to R-alkanes. We believe that the
  alkane-alkane density, averaged over all angles, is the feature most likely to be
  replicated between experiment and simulation. Other features are dependent on 
  system ordering which is likely to have some dependence on initial configuration. 
  We calculated the average intensity within R-alkanes of the experimental pattern,
  $I_{avg}$ and divided all intensities by this value. In this way, the average intensity
  of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded intensities 
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the simulated
  patterns differ from experiment in those regions in all cases. Specifically, in contrast
  to the experimental WAXS pattern, R-$\pi$ as it appears the simulated diffraction 
  patterns intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
  an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly. 
  We applied the same scaling method to the simulated patterns. We carefully chose a scaling
  factor of $f=3.1$ in order to visibly display all features in all patterns.

@@

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). The remainder of this discussion will focus on the analysis of
  systems built with 5 columns per pore. Ordered basin systems built with 6 columns per pore,
  have an equilibrated pore spacing ca. 0.50 nm higher than experiment. Ordered basin systems
  built with 4 columns per pore equilibrate to an average pore spacing 0.25 nm lower than experiment.

  %BJC5: thesis needs rewording.
  Monomers in disordered basin systems built with 6 columns-per-pore stack too far apart.
  Those in the disordered sandwiched and disordered parallel displaced configurations stack 
  $\approx$ 4.87 and 4.94~\AA apart respectively, which is ca. 1.2~\AA further apart than 
  suggested by experiment. 5 column-per-pore systems stack, at a maximum, 0.9 ~\AA further
  apart than experiment (see Table~\ref{table:correlation_length}). Methodology for calculating
  equilibrium stacking distance is fully explained in section~\ref{section:rpi}.

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
  maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

  The simulated XRD patterns of the parallel displaced configurations show an additional
  reflection due to their helical structure. There are horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
  This type of pattern is characteristic of a helix ~\cite{watson_structure_1953}. The 
  head groups in the parallel displaced configuration are arranged in a helix.
  It is possible that these reflections contribute to the diffuse reflections that connect
  R-spots and R-double in the experimental pattern.

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
  identified spots based on visual inspection. If the spots were not easily discernible, then the 
  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
  lower than experiment in all cases. There is no R-double intensity to be measured. Figures
  are provided in section S\ref{S-section:xrd_intensities} to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  %BJC6: yea, specifically the one for j phys chem B. I compiled with a different document type and the captions looked normal
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore the possible origin of each experimental reflection and form 
  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
  want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

  To understand the true origin of R-spots, we determined which atoms gave rise to the 
  feature. Since R-spots is present as higher intensity spots within R-alkanes, it is
  likely that the spots arise as a consequence of the tails. By removing all non-tail atoms
  from the trajectory and simulating a diffraction pattern with the remaining atoms, we were
  able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the 
  tails stay nearly flat, we plotted the centroids of the tails (Figure \ref{fig:centroids})
  and measured the angle between each centroid and its nearest neighbors with respect to the 
  plane of the membrane. We see distinct peaks in the distribution of these angles 
  (Figure~\ref{fig:tail_packing}).

@@

  There is not a single reason for the high intensity of R-$\pi$ in our simulations.
  We used one-dimensional pair distribution functions of the centers of masses of monomer
  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
  columns and the degree to which they are correlated. These metrics helped us disect the 
  various contributions to R-$\pi$. Figure ~\ref{fig:correlation} shows $g(z)$ for all 
  systems tested.

@@

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough to create the noise which would 
  cause such behavior. See Section S\ref{S-section:rpi_ft} of the supporting information for
  illustrative examples.

>>>>

  The H\textsubscript{II} phase pore geometry has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains, created by the monomer Na-GA3C11,
  using a magnetic field with subsequent cross-linking to lock the structure in 
  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
  Current experimental efforts are focused on extending the method to the 
  H\textsubscript{II} phase and characterizing the performance of these newly aligned systems.

@@

  In this paper, we develop a molecular model of the Col\textsubscript{h} assembly 
  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which allowed us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. We will use this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to real
	space periodicity of 7.4 \AA. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
	relative intensity.  Accordingly, we name these reflections R-spots. The
	location of all spots is $\sim\;37^{\circ}$ from the $q_z$ axis in their
	respective quadrants. In many liquid crystal systems one can explain the spots
	as the product of alkane chains tilted with respect to the membrane
	plane\cite{govind_simple_2001}.

@@

    %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
    % in many liquid crystal systems?
    %BJC5: changed to 'many liquid crystalline systems'
 	We are careful to avoid the term 'layers' since many liquid crystalline systems
 	have long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range z-direction correlations between 
        stacked columns of monomers. In this study, we use our atomistic molecular model
        to study how the system's structure is affected by the density of these monomer columns
        that surround each pore's hydrophilic core.

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water are leached into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
	to see if there is any meaningful structural difference between a "dry" and a "wet" system.

@@

	The limited picture that experiment provides tells us that there are hexagonally packed, 
	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
	regions as tube-like pathways with well-defined boundaries. We explored the composition
	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
	sensitivity to initial configuration, including both dry and wet systems.

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended
  periodically. Each pore is made of columns of stacked monomers with periodic
  continuity along the pore axis, avoiding any edge effects and creating an
  infinite length pore ideal for studying transport. We prefer a small number of stacked
  monomers in order to reduce computational cost and to allow us to look at
  longer timescales. Ultimately, we chose to build a system with 20 monomers
  per column in order to minimize finite size effects with reasonable computational expense 
  and to obtain sufficient resolution when simulating XRD patterns (see further discussion
  in section S\ref{S-section:monomers_per_column}).

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. The initial distance between pores, within a wide range, also has 
  little effect on the the equilibrated structure. However, one should not start them
  too close or there will be high energy repulsions during early equilibration. We 
  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
  Supporting information, section S\ref{S-section:initial_config_dependence}. The 
  distance between vertically stacked monomers, the xy position of monomers with respect 
  to vertically adjacent monomers, and the number of columns per pore do influence the 
  equilibrated structure and require further justification for their choices. We rely on 
  experimental data to inform them.

  We chose the vertical spacing between monomers for the initial configuration based
  on R-$\pi$ and then allowed the system to readjust during equilibration. We rotated 
  each monomer so the plane of its aromatic head group would be coplanar with the xy plane. We
  explored three different initial monomer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial spacing of 5
  \AA. We briefly explored a third system with an initial spacing of 10
  \AA. However this spacing yields non-physical behavior which is detailed in the 
  Supporting Information, section S\ref{S-section:initial_dbwl}.

@@

  \subsection{Equilibration}
  %MRS7: could put this mostly in supporting. 
  %BJC6: cut in half
  We developed equilibration schemes for creating dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. For wet systems, we added the desired concentration of water to 
  the initial configuration and carried out equilibration in the same way
  as the dry systems. First, we fixed monomer head groups in place using position
  restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We gradually
  released the position restraints by decreasing the force constants over a series
  of NVT simulations. We allowed the resulting unrestrained structure to equilibrate for
  5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
  followed by NPT equilibration simulations run for at least 400 ns using the 
  Parrinello-Rahman barostat. More precise details are available in 
  section S~\ref{S-section:equilibration}.

@@

  Here, $g(z)$ is characterized by an oscillatory function with a period equal to the
  average distance between stacked monomers, and an amplitude that decays exponentially
  (See Figure~\ref{fig:correlation}). The rate of decay is related to the correlation 
  length, L, between monomer head groups. We estimated L by fitting the peaks of $g(z)$
  to a decaying exponential function of the form:
  \begin{equation}
  	Ae^{-z/L}
  	\label{eqn:decaying_exponential}
  \end{equation}
  where A is a fitting parameter for amplitude, z is the independent variable of $g(z)$ 
  and L is the fit correlation length. We calculated the error in the estimated value
  of L as the square root of the diagonal entry of the covariance matrix of 
  optimized fit parameters.  %BJC6: reference scipy curve_fit?

@@

  We explored the pores' compositions by measuring the average number densities
  of various monomer components as a function of distance from the pore centers.
  We looked at the average number density of sodium ions, aromatic rings and 
  carbon atoms making up the monomer tails. We binned the radial distance of all
  atoms in each group from the pore centers, then normalized by the volume of the
  annulus defined by the bin edges and the z box vector (See Figure~S\ref{S-fig:rdf_diagram}).

@@

  We normalized all diffraction patterns relative to R-alkanes. We believe that the
  alkane-alkane density, averaged over all angles, is the feature most likely to be
  replicated between experiment and simulation. Other features are dependent on 
  system ordering which is likely to have some dependence on initial configuration. 
  We calculated the average intensity within R-alkanes of the experimental pattern,
  $I_{avg}$ and divided all intensities by this value. In this way, the average intensity
  of R-alkanes was equal to 1. When calculating $I_{avg}$, we excluded intensities 
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the simulated
  patterns differ from experiment in those regions in all cases. Specifically, in contrast
  to the experimental WAXS pattern, R-$\pi$, as it appears in the simulated diffraction 
  patterns, intersects with R-alkanes (See Figure~\ref{fig:XRDsim}). We set
  an upper bound on the colorbar by multiplying $I_{avg}$ by a scaling factor, $f$. 
  Intensities that appear in the patterns $\geq$ $f\times I_{avg}$ are colored uniformly. 
  We applied the same scaling method to the simulated patterns. We carefully chose a scaling
  factor of $f=3.1$ in order to visibly display all features in all patterns.

@@

  Systems built with 5 columns in each pore equilibrate to a pore spacing that is most 
  consistent with the experimental value of 4.12 nm derived from SAXS measurements 
  (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4 columns per pore equilibrate
  to an average pore spacing 0.25 nm lower than experiment. Ordered basin systems built with
  6 columns per pore, have an equilibrated pore spacing ca. 0.50 nm higher than experiment.
  Monomers in disordered basin systems built with 6 columns-per-pore agree with experiment 
  within error, but stack too far apart. Those in the disordered sandwiched and disordered
  parallel displaced configurations stack $\approx$ 4.87 and 4.94 \AA~apart respectively, 
  which is ca. 1.2~\AA further apart than suggested by experiment. 5 column-per-pore systems
  stack, at a maximum, 0.9 \AA~further apart than experiment (see Table~\ref{table:correlation_length}). 
  The remainder of this discussion will focus on the analysis of systems built with 5 columns per pore.

% BJC6: I don't think I need to say the following in above paragraph since its all in the methods.
% Our methodology for calculating equilibrium stacking distance is fully explained in section~\ref{section:rpi}.

@@

  The simulated XRD patterns show moderate qualitative agreement with experiment. R-alkanes and
  R-pores appear in the expected location. R-pores is more intense than experiment, likely
  because we are simulating a near perfect, infinite hexagonal array. The real system has 
  defects and domain misalignment which decreases the overall intensity.
  % MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for 
  % the difference in intensity ratio. Some of the experiments should help explain it better. 	
  % Let's talk!
  % BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
  % pores in unit cell, tortuosity (?)
  % MRS5: maybe, there's a question of how we can demonstrate the magnitude of any of these 
  % effects.
  R-spots appears to be weaker, except for the ordered basin sandwiched configuration, in the 
  simulated patterns. R-spots is also partially engulfed by the wide R-$\pi$ reflection. R-$\pi$
  appears at a lower $q_z$ value than experiment. In all systems, the reflection reaches its 
  maximum at $q_z < 1.5~\AA^{-1}$ which means that monomers prefer to stack at least 4.2 \AA~apart
  rather than 3.7 \AA. R-double does not appear in any of the patterns.

@@

  The simulated XRD patterns of the parallel displaced configurations show an additional
  reflection due to their helical structure. There are weak horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
  This type of pattern is characteristic of a helix ~\cite{watson_structure_1953}. The 
  head groups in the parallel displaced configuration are arranged in a helix.
  It is possible that these reflections contribute to the diffuse reflections that connect
  R-spots and R-double in the experimental pattern.

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
  identified spots based on visual inspection. If the spots were not easily discernible, then the 
  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
  agrees with experiment. There is no R-double intensity to be measured. Figures
  are provided in section S\ref{S-section:xrd_intensities} to make these measurements clear.

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		   & \multicolumn{5}{c}{Configuration} \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      & 1.0        & 1.0                \\  
  R-spots    & 1.3        &  1.3       &  1.2      & 1.1        & 1.2                \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      & 8.4        & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
  \caption{The simulated XRD patterns of the systems tested, normalized so that the average 
  intensity of R-alkanes equals 1, show R-$\pi$ reflections that are significantly higher 
  than experiment and R-spots reflections that are slightly lower than experiment. R-double
  does not appear in any patterns, and thus has no measurable intensity.}
  \label{table:relative_inensities_300K} 
  \end{table}
  %BJC5: Bold font is caused by achemso document type
  %MRS7: huh.
  %BJC6: yea, specifically the one for j phys chem B. I compiled with a different document type and the captions looked normal
  There are clear differences between simulated and experimental results that must be addressed
  and justified. We will explore the possible origin of select experimental reflections and form 
  structural hypotheses related to their appearance in our simulated patterns. Specifically, we 
  want answer:  
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-double?
  \end{enumerate}

@@

  To understand the true origin of R-spots, we determined which atoms gave rise to the 
  feature. Since R-spots is present as higher intensity spots within R-alkanes, it is
  likely that the spots arise as a consequence of the tails. By removing all non-tail atoms
  from the trajectory and simulating a diffraction pattern with the remaining atoms, we were
  able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the 
  tails stay nearly flat, we plotted their centroids (Figure \ref{fig:centroids})
  and measured the angle between each centroid and its nearest neighbors with respect to the 
  plane of the membrane. We see distinct peaks in the distribution of these angles 
  (Figure~\ref{fig:tail_packing}).

@@

  There is not a single reason for the high intensity of R-$\pi$ in our simulations.
  We used one-dimensional pair distribution functions of the centers of masses of monomer
  phenyl groups, $g(z)$, to help us understand how far apart monomers stack within monomer 
  columns and the degree to which they are correlated. These metrics helped us disect the 
  various contributions to R-$\pi$. Figure~\ref{fig:correlation} shows $g(z)$ for all 
  systems tested.

@@

  The persistent oscillatory behavior of the correlation function may in part explain the high
  intensity of R-$\pi$ relative to experiment. The way we calculate correlation length is
  unique to the rate of decay of $g(z)$ but not its exact shape. $g(z)$ for our 
  simulated systems, especially the sandwiched configurations, shows peaks which persist across
  the entire correlation function. If the peaks, at large values of z, instead decay to 1 uniformly,
  the correlation length could remain nearly the same, but R-$\pi$ would have a reduced intensity. 
  The monomer head groups in our simulations do not move enough on the timescales simulated to 
  create the noise which would cause such behavior. See Section S\ref{S-section:rpi_ft} of the
  supporting information for illustrative examples.
